Unimodular covers of 3-dimensional parallelepipeds and Cayley sums

### 2019-07-07 unimodular-covers.tex

This not only implies \Cref{conj:Oda}\eqref{itm:mixedIDP} in dimension two but also, as we show in \Cref{sec:cayley}, \Cref{conj:Oda}\eqref{itm:smoothIDP} for $3$-dimensional smooth \emph{prismatoids}, polytopes whose vertices all lie in two parallel facets:

@@

Consider the segment $s$ contained in $r_1' + \vecline p$ with endpoints $s_1=r_1'$ on $d$ and $s_2$ on $d'$.

%By claim \ref{claim:r}, $s_2$ lies above the affine line $\langle t \rangle$.

Since $t$ separates $q_1$ and $q_1+q_2-p_1$ and $g$ decreases from $t_1$ to $t_2$ (by \Cref{claim:g}), the inequality $g(x)< g(d')$ holds on $Q\cap V_2$,
and in particular for $r_2'$. Since $r_2'$ is a lattice point, $g(r_2')\leq g(d)= g(r_1')$, which contradicts \Cref{claim:g}).
\end{proof}
\giulia{add a picture!}

>>>>

This not only implies \Cref{conj:Oda}(1) in dimension three, but also the following two statements, that we prove in \Cref{sec:cayley}.
A $3$-dimensional \emph{prismatoids} is a polytopes whose vertices all lie in two parallel facets. A special case is a polytope of width $1$, whose vertices lie in two consecutive parallel lattice hyperplanes.

@@

Consider the segment $s$ contained in $r_1' + \vecline p$ with endpoints $s_1=r_1'$ on $d$ and $s_2$ on $d'$.  
Since $t$ separates $q_1$ and $q_1+q_2-p_1$ and $g$ decreases from $t_1$ to $t_2$ (by \Cref{claim:g}), the inequality $g(x)< g(d')$ holds on $Q\cap V_2$,
and in particular for $r_2'$. Since $r_2'$ is a lattice point, $g(r_2')\leq g(d)= g(r_1')$, which contradicts \Cref{claim:g}).
\end{proof}
\giulia{add a picture!}
